Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-19 paper/paper.tex
Added text to airframe section, still needs work

\documentclass[12pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous}

@@

\subsection{Airframe}

@@

\section{Autopilot}

@@

\subsection{Hardware Design}

\subsection{Software Design}

@@

>>>>

\documentclass[10pt]{report}
\usepackage[pdftex]{graphicx}
\usepackage{hyperref}
\hypersetup{ colorlinks=true
           , linkcolor=cyan
           , pdfnewwindow=true 
           }
\usepackage{amsmath}
\usepackage{subfig}
\usepackage{listings}
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\hyphenation{auto-nomous}

% Limited by competition rules to min font size 10 pt, max pages 20

@@

\subsection{Airframe}
The Rutgers team, after much deliberation, elected to persue a kit-type airplane rather than an in-house design.  This decision was based on a thorough analysis of available time and materials: though an in-house design is always preferred, it was quickly determined that the team, in its second year, did not yet posses the time or expertise required for a project of such enormity.  Eager to avoid mistakes made in the previous year that resulted in a catastrophic crash mere weeks before  competition, the team gladly accepted an already-constructed plane from a local RC club.  The donating member intimated that the model was in good, ready-to-fly condition, requiring only minimal repairs.  Upon further inspection, the team readily came to the conclusion that, unfortunately, a significant remodel was necessary: wood was rotted out, foam eaten away, and necessary structural members non-existant.

@@

\section{Autopilot}
Our entry uses an autopilot system based off the open source 
Paparazzi project\cite{paparazziweb}. 
We ported the airborne code to Linux in order to use a single computer for all of our flight hardware and software.

@@

We needed to interface with the following hardware components:
\begin{itemize}
	\item GPS
	\item servos
	\item etc.
\end{itemize}

\subsection{Hardware}

\subsection{Software}

@@

\bibliographystyle{plain}
\bibliography{paper}
